---
title: "Gathering QWI Data Over Several Years for Multiple States"
author: "Mona Ahmadiani"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

Sometimes one may want to collect data from multiple states over multiple years. To do this we recommend loading the following libraries:

```{r eval=FALSE}
library(future)
library(tidyqwi)
library(purrr)
library (tidyverse)
```

Then we can create the different combinations of year and state in order to submit to `tidyqwi.`


```{r eval=FALSE}
year <- c("2008", "2009", "2010","2011")
state <- c("01","02","04","05","06","08","09","10","11","12",
           "13","15","16","17","18","19","20","21","22","23",
           "24","25","26","27","28","29","30","31","32","33",
           "34","35","36","37","38","39","40","41","42","44",
           "45","46","47","48","49","50","51","53","54","55",
           "56")

argList <- list(x = state, y = year)

arguments <- cross_df(argList)
```

Using the multiple processing function we can submit the following:

```{r eval=FALSE}
plan("multiprocess")

qwi_data <- map2(arguments$x, arguments$y, ~
                  get_qwi(
                    states = .x,
                    years  = .y ,
                    industry_level = "2",
                    all_groups = FALSE,
                    endpoint = "se",
                    geography = "cbsa",
                    processing = "multiprocess",
                    apikey = APIkey))
```

After this function returns out values we can collapse these data into a single data set.

```{r eval = FALSE}
qwi_data <- purrr::map_dfr(qwi_data, as_tibble)

```

And then add the labels for our variables if desired.

```{r eval=FALSE}
qwi_data <- add_qwi_labels(qwi_data)
```


